Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-10 manuscript/manuscript.Rmd
glm

1. A GLM with gamma distribution and log link function
2. A linear model with categorical embeddings and an exponential output activation
3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2
4. A multilayer perceptron regression model

@@

While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
reference since most actuaries are familiar with the technique. 
While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of establishing a
baseline model, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:

-   Target variable: Amount paid on building claim
-   Predictors: *Log* of **building insurance coverage**, **basement enclosure type**, **number of floors in the insured building**, *prefix* of **flood zone**, and ***primary residence***.
-   Link function: log
-   Distribution: gamma

We take the log of the continuous predictor **building insurance coverage**, which allows the scale of the predictor to 
match that of the target variable. Because the **flood zone** variable in the original data contains 60 levels, we take 
the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, *A01*, 
*A02*, and so on are recoded as simply *A*.

>>>>

In this subsection, we develop the following models:

1. A GLM with gamma distribution and log link function,
2. A linear model with categorical embeddings and an exponential output activation,
3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2, and
4. A multilayer perceptron model with categorical embeddings.

These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
embedding components. Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings
that represent the state of the art for modeling tabular data.

@@

While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
reference since most actuaries are familiar with the technique. 
Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to 
be made in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of 
establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:

-   Target variable: Amount paid on building claim
-   Predictors:
    - $\log$ `building_insurance_coverage`
    - `basement_enclosure_type`, 
    - `number_of_floors_in_the_insured_building`
    - *prefix* of `flood_zone`
    - `primary_residence`
-   Link function: $\log$
-   Distribution: gamma

We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
`"A02"`, and so on are recoded as simply `"A"`.
